A Formal Model of Checked C

### 2023-01-20 sandp23/evaluation.tex
Adding experiemnt results

\subsection{Dataset}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

\noindent\textbf{Overhead of only~\systemname{}.}
To verify the impact of the sandbox on the overall program runtime, we perform a NO-OP sandbox experiment.
Our goal is to measure the runtime overhead introduced ONLY by~\systemname{}.
We perform this experiment by skipping sandboxing.
Specifically, we run the completely annotated program as a regular application without any partitioning.
However, we compile the annotated program with~\systemname compiler, which will add the relevant runtime checks (\sect{subsec:compilerimple}).
We modify the instrumentation on~\code{taint}ed pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.

The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.
%\aravind{Arun, we should do this experiment. This should be fairly easy.}

>>>>

\subsection{Dataset}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

\noindent\textbf{Overhead of only~\systemname{}.}
To verify the impact of the sandbox on the overall program runtime, we perform a NO-OP sandbox experiment.
Our goal is to measure the runtime overhead introduced ONLY by~\systemname{}.
We perform this experiment by skipping sandboxing.
Specifically, we run the completely annotated program as a regular application without any partitioning.
However, we compile the annotated program with~\systemname compiler, which will add the relevant runtime checks (\sect{subsec:compilerimple}).
We modify the instrumentation on~\code{taint}ed pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.
~\paragraph{Results:}
Our evaluation of ~\systemname{} with NO-OP Sandbox was performed on two programs with the largest overheads in our dataset. With parsons, we see an average run-time overhead of 1.94\% as is expected as parsons (($T_{Pr}$)) gave us an overhead of only 9\%. With TinyBigNum, we see an overhead of 54.7\%, and is expected referring to the figure ~\ref{fig:microbenchmarks}, as TinyBigNum is pointer intensive with pointer operations inside nested loops.     
The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.
